\documentclass[12pt]{book}
\title{Rush}
\author{Jorin Gedamke}

\begin{document}
\maketitle
\mainmatter
\chapter{Red Alert}


The klaxon brought Rush instantly, no doubt thanks to her training.
She sprang out of her bunk, instinctively reaching for her armor and weapons.

Some of her fellow cadets were slower to rouse. A few slept in only their fur, in defiance of regs.
She frowned briefly at them.

``Rise and shine, sweethearts! This is not a drill.'' Sergeant Vedran glared at the delinquents. ``You ladies'd better get dressed.
We've spotted a Drail ship that's unaware of our presence... for now.''

\emph{The Drail!} Rush's already-thumping heart sped up a notch; she almost let out an excited chirp.
Her kind, in the form of the Otter Space Force, had been at war with the badger-like Drail for almost seven years now.
She wasn't entirely sure why.

``Sarge? It's a real raid this time?'' This from Kitsa, the youngest cadet by almost a year.

``That's right, missy.'' Vedran gave her a reassuring wink. ``Ten to one there'll be no boarding action---
but it never hurts to be prepared.''

Rush mentally echoed that last phrase- the sergeant's mantra on this cruise.
Though she was scared, she hoped there {\em was} a boarding action.

Otherwise, what was all their preparation for?

\chapter{Captured}

Rush hadn't spent much time in the infirmary, but the steady beeping of a heart monitor was unmistakable.

``Who's hurt?'' she mumbled, and then wondered why her voice sounded so odd.

``You are, cadet.'' The rumbling, unfamiliar voice made her eyes snap open.

Someone touched her right shoulder. She looked up, dreading what she'd see.

A Drail loomed over her---a male with the blue triangle signifying ``medic'' tattooed on his cheek.
{\em But am I in the sickbay or the brig---and how did I get here?}

``M-my ship?'' She hated the way her voice broke.

``Suffered only minor damage. Now lie still.''

Easy for him to say. He wasn't lying in bed on a strange ship with pain flashing through his chest.

``They say that where there's life there's hope, cadet.''

She glared up at him. ``My name is Rush.''

Her eyes opened like clockwork---0600, time to get up.

\end{document}
% Do some reasearch, then write about the battle.