\documentclass{book}
\begin{document}
With nothing to do, Rush found her thoughts turning inward---and then, not liking what she saw, upward.

``I'm afraid. So far the Drail have treated me well, but I'm still a prisoner aboard an enemy ship.

``God, what if I'm interrogated? I'm just a cadet; I don't know any military secrets.''

``You're not `just' anything, Rush.''

Startled, she reached for her sidearm---which, of course, wasn't there.

``Sorry! I should know better by now.''

Rush took a deep breath, then patted the bed beside her.

``Thanks. I've been at work all morning and my back is killing me.'' Jay smiled ruefully. ``It would seem you have as much on your mind as I do 
on my back, so let's talk.''

Without being asked, Rush started to massage her friend's broad shoulders.

``You're full of surprises,'' Jay grunted approvingly. ``Which reinforces my point: you're not `just' a cadet, or anything else.''

``I guess so.''

\section{Nightmares}
The heart monitor infiltrated Rush's dreams. She relived the boarding action, its utter chaos out of sync with that monotonous rhythm.

Again the enemy took aim at her. She could do nothing but mouth a prayer before the beam reached her---

``Cadet! Wake up; you are having a nightmare.''

Before she could think, she lashed out at the voice's source.

``I am not your enemy. Wake up.''

She opened her eyes to find ``her'' medic standing just out of reach. His frown distorted the tattoo that had been her first glimpse of him.

We really must stop meeting like this, she thought with a wry twist of her mouth.

``You're awake- good,'' he said, his frown easing. ``What was your dream about?''

Rush told him.

\end{document}